Incorporating periodic variability in hidden Markov models for animal movement

### 2016-04-11 paper3.Rnw
small changes

<<adj_BIC_comparisons, warning=FALSE, echo=FALSE, message=FALSE,fig.cap="Overall adjusted BIC comparisons among models",fig.width=8>>=
L <- load("cat1sumdat.RData")
(adj_BIC_plot <- ggplot(sumdat, aes(x=nstates,y=deltaBIC,colour=model))+
    facet_wrap(~ type,ncol=4)+
    scale_size_continuous( name="# of parameters") +
    scale_x_continuous(expand=c(0,0.5),breaks=2:6)+
    geom_point(aes(size=parameters))+
    scale_colour_brewer(palette="Dark2")+
    labs(y=expression(paste(Delta, "BIC")),
         x="Number of States") +
    geom_line() + zmargin)
@

@@

\begin{table}[]
\centering
\caption{Number of Parameters for each model type.
\textbf{todo: add general formula for each model type, e.g. FMM = $S$ (occupancies) + $2S$ (emissions: mean and std dev for each state); HMM = $S(S-1)+2S=S^2+S$.  Be clear about whether we're talking about restricted (constrained) or unconstrained.}
}
\label{npartab}
\begin{tabular}{cccc}
 Type & Model  & Number of States & Number of Parameters  \\
  FMM & FMM & 3 & 9    \\
  FMM & FMM & 4 & 12    \\
  FMM & FMM & 5 & 15   \\
  FMM & FMM & 6 & 18  \\
  FMM + TH & FMM + TH (Sin)  & 3 & 15    \\
  FMM + TH & FMM + TH (Sin)  & 4 & 20    \\
  FMM + TH & FMM + TH (Sin)  & 5 & 25    \\
  FMM + TH & FMM + TH (Sin)  & 6 & 30    \\
  HMM & HMM & 3 & 18    \\
  HMM & HMM & 4 & 28    \\
  HMM & HMM & 5 & 40   \\
  HMM & HMM & 6 & 54  \\
  HMM + TH & HMM + TH (Block)  & 3 & 36    \\
  HMM + TH & HMM + TH (Block)  & 4 & 60    \\
  HMM + TH & HMM + TH (Block)  & 5 & 90    \\
  HMM + TH & HMM + TH (Block)  & 6 & 126    \\
  HMM + TH & HMM + TH (Quad)  & 3 & 36    \\
  HMM + TH & HMM + TH (Quad)  & 4 & 60    \\
  HMM + TH & HMM + TH (Quad)  & 5 & 90    \\
  HMM + TH & HMM + TH (Quad)  & 6 & 126    \\
  HMM + TH & HMM + TH (Sin)  & 3 & 36    \\
  HMM + TH & HMM + TH (Sin)  & 4 & 60    \\
  HMM + TH & HMM + TH (Sin)  & 5 & 90    \\
  HMM + TH & HMM + TH (Sin)  & 6 & 126    \\
  HMM + TH & HMM + TH (Hourly)  & 3 & 225    \\
  HMM + TH & HMM + TH (Hourly)  & 4 & 396    
\end{tabular}
\end{table}

>>>>

<<adj_BIC_comparisons, warning=FALSE, echo=FALSE, message=FALSE,fig.cap="Overall adjusted BIC comparisons among models",fig.width=8>>=
L <- load("cat1sumdat.RData")
(adj_BIC_plot <- ggplot(sumdat, aes(x=nstates,y=deltaBIC,colour=model))+
    facet_wrap(~ type,ncol=4)+
    scale_size_continuous( name="# of parameters") +
    scale_x_continuous(expand=c(0,0.5),breaks=2:7)+
    geom_point(aes(size=parameters))+
    scale_colour_brewer(palette="Dark2")+
    labs(y=expression(paste(Delta, "BIC")),
         x="Number of States") +
    geom_line() + zmargin)
@

@@

\begin{table}[]
\centering
\caption{Number of Parameters for each model type.
\textbf{todo: add general formula for each model type, e.g. FMM = $S$ (occupancies) + $2S$ (emissions: mean and std dev for each state); HMM = $S(S-1)+2S=S^2+S$.  Be clear about whether we're talking about restricted (constrained) or unconstrained.}
}
\label{npartab}
\begin{tabular}{cccc}
 Type & Model  & Number of States & Number of Parameters  \\
  FMM & FMM & 3 & 8    \\
  FMM & FMM & 4 & 11    \\
  FMM & FMM & 5 & 14   \\
  FMM & FMM & 6 & 17  \\
  FMM & FMM & 7 & 20  \\
  FMM + TH & FMM + TH (Sin)  & 3 & 12    \\
  FMM + TH & FMM + TH (Sin)  & 4 & 17    \\
  FMM + TH & FMM + TH (Sin)  & 5 & 22    \\
  FMM + TH & FMM + TH (Sin)  & 6 & 27    \\
  FMM + TH & FMM + TH (Sin)  & 7 & 32    \\
  HMM & HMM & 3 & 14    \\
  HMM & HMM & 4 & 23    \\
  HMM & HMM & 5 & 24   \\
  HMM & HMM & 6 & 47  \\
  HMM & HMM & 7 & 62  \\
  HMM + TH & HMM + TH (Block)  & 3 & 26    \\
  HMM + TH & HMM + TH (Block)  & 4 & 47    \\
  HMM + TH & HMM + TH (Block)  & 5 & 74    \\
  HMM + TH & HMM + TH (Block)  & 6 & 107    \\
  HMM + TH & HMM + TH (Block)  & 7 & 146    \\
  HMM + TH & HMM + TH (Quad)  & 3 & 26    \\
  HMM + TH & HMM + TH (Quad)  & 4 & 47    \\
  HMM + TH & HMM + TH (Quad)  & 5 & 74    \\
  HMM + TH & HMM + TH (Quad)  & 6 & 107    \\
  HMM + TH & HMM + TH (Quad)  & 7 & 146    \\
  HMM + TH & HMM + TH (Sin)  & 3 & 26    \\
  HMM + TH & HMM + TH (Sin)  & 4 & 47    \\
  HMM + TH & HMM + TH (Sin)  & 5 & 74    \\
  HMM + TH & HMM + TH (Sin)  & 6 & 107    \\
  HMM + TH & HMM + TH (Sin)  & 7 & 146    \\
  HMM + TH & HMM + TH (Hourly)  & 3 & 152    \\
  HMM + TH & HMM + TH (Hourly)  & 4 & 299    
\end{tabular}
\end{table}
